### 2011-01-21 paper/problemDefinition.tex
Done with Problem Definition for now

\section{Problem definition}
% Precisely define the problem you are addressing (i.e. formally specify
% the inputs and outputs). Elaborate on why this is an interesting and
% important problem.

\edit{write this.  Quadratot report section below}

We are testing several different learning methods to design a
parametrized gait for a quadruped robot from the Cornell Computational
Synthesis Lab.

The output each of the learning algorithms is a function of time,
$f(t)$, that outputs a vector of commanded motor positions.  This
function is generated using a parametrized motion model, described in
\secref{implement}.

The robot executes these commands and measures its change in location
using the tracking system described in \secref{implement}.  The input
to the learning algorithms is this measured displacement, which the
algorithms attempt to maximize. This displacement is measured for each
gait over a constant length run, usually 12 seconds.

A comparison and evaluation of the many different methods available
for optimizing the gait of legged robots will be useful for future
work on this challenging multidimensional control problem.

\edit{Jason writing this now}

@@

The ultimate goal was to design gaits that were as fast as possible,
so to optimize for speed, our performance metric was displacement over
a period of motion lasting approximately 10 seconds.  For details of
exactly how this displacement was measured, see \secref{foo}.

>>>>

\section{Problem definition}
% Precisely define the problem you are addressing (i.e. formally specify
% the inputs and outputs). Elaborate on why this is an interesting and
% important problem.
%
%\edit{write this.  Quadratot report section below}
%
%We are testing several different learning methods to design a
%parametrized gait for a quadruped robot from the Cornell Computational
%Synthesis Lab.
%
%The output each of the learning algorithms is a function of time,
%$f(t)$, that outputs a vector of commanded motor positions.  This
%function is generated using a parametrized motion model, described in
%\secref{implement}.
%
%The robot executes these commands and measures its change in location
%using the tracking system described in \secref{implement}.  The input
%to the learning algorithms is this measured displacement, which the
%algorithms attempt to maximize. This displacement is measured for each
%gait over a constant length run, usually 12 seconds.
%
%A comparison and evaluation of the many different methods available
%for optimizing the gait of legged robots will be useful for future
%work on this challenging multidimensional control problem.

@@

The ultimate goal was to design gaits that were as fast as possible,
so to optimize for speed, our performance metric was displacement over
a period of motion lasting approximately 10 seconds.  For details of
exactly how this displacement was measured, see
\secref{fitnessEvaluation}.
